Does a fully convective star need a special corona to produce a polar flare?

### 2023-08-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@

%\affiliation
\newcommand{\T1}{\input{output/T1.tex}}
\newcommand{\T2}{\input{output/T1.tex}}

@@

From the XMM-Newton EPIC spectra, we could measure the coronal properties of TIC in both its quiescent, and flaring states~(Table~\ref{tab:specfit}). Using the combined quiescent and flaring data, we found a two-temperature VAPEC model to fit better than a one-temperature solution and no worse than a three-temperature solution. The resulting fit~(Fig.~\ref{fig:spec_joint_all}) consists of a cooler and a hotter component of about $\T1\,$MK and $\T2\,$MK, respectively. With these temperatures as ground truth, we also fitted two-temperature VAPEC models to the flaring and quiescent portions of the observations separately. The coronal temperatures did not update significantly using either subset, although the quiescent spectrum appeared slightly cooler overall. However, the emission measure weighted mean temperature was about $1.5\,$MK cooler in the quiescent spectrum, and $\sim3.2\,$MK hotter in the flaring spectrum. This suggests that the flaring corona emits the hotter component, while the cooler component corresponds to the quiescent corona. In this interpretation, the presence of a hot component in the quiescent spectrum indicates that TIC 277 is flaring below the detection threshold, consistent with an extrapolation of the flare frequency distribution to lower temperatures~(see the following Section, and Fig.~\ref{fig:ffd}).

>>>>

\newcommand{\Tcool}{\input{output/T1.tex}}
\newcommand{\Thot}{\input{output/T2.tex}}

@@

%\affiliation
\author[0000-0002-6299-7542]{Ekaterina Ilin}
\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}

\author[0000-0003-1231-2194]{Katja Poppenh\"ager}
\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
\affiliation{Institute for Physics and Astronomy, University of Potsdam, Karl-Liebknecht-Strasse 24/25, 14476 Potsdam, Germany}

\author[]{Beate Stelzer}
\affiliation{Institut für Astronomie & Astrophysik, Eberhard-Karls-Universität Tübingen, Sand 1, 72076 Tübingen, Germany}
\affiliation{INAF – Osservatorio Astronomico di Palermo, Piazza del Parlamento 1, 90134 Palermo, Italy}

@@

From the XMM-Newton EPIC spectra, we could measure the coronal properties of TIC in both its quiescent, and flaring states~(Table~\ref{tab:specfit}). Using the combined quiescent and flaring data, we found a two-temperature VAPEC model to fit better than a one-temperature solution and no worse than a three-temperature solution. The resulting fit~(Fig.~\ref{fig:spec_joint_all}) consists of a cooler and a hotter component of about \Tcool and \Thot, respectively. With these temperatures as ground truth, we also fitted two-temperature VAPEC models to the flaring and quiescent portions of the observations separately. The coronal temperatures did not update significantly using either subset, although the quiescent spectrum appeared slightly cooler overall. However, the emission measure weighted mean temperature was about $1.5\,$MK cooler in the quiescent spectrum, and $\sim3.2\,$MK hotter in the flaring spectrum. This suggests that the flaring corona emits the hotter component, while the cooler component corresponds to the quiescent corona. In this interpretation, the presence of a hot component in the quiescent spectrum indicates that TIC 277 is flaring below the detection threshold, consistent with an extrapolation of the flare frequency distribution to lower temperatures~(see the following Section, and Fig.~\ref{fig:ffd}).
